---
title: "Unlocking Superconductor Potential: Predicting Critical Temperatures with Multivariate Regression"
author: "Alina Yildir UCID: 30271992, Archana Senthil UCID: 30265251, Gurmol Sohi UCID: 10174773, Trevor Yonkman UCID: 30271573, William Hovdestad UCID: 30248416"
output: pdf_document
date: "2024-11-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. INTRODUCTION

## 1.1. MOTIVATION

### 1.1.1. Context

Certain materials exhibit the property of superconductivity, meaning that, under certain conditions, they can carry an electrical current with no losses. Since the discovery of the first superconductor in 1911 [1], which showed these properties in mercury below a Critical Temperature (Tc) of 4.2 Kelvin (-269 °C), researchers have looked for materials with superconducting properties at higher and higher temperatures. Applications of superconductors include medical imaging [2] and quantum computing [3], with each becoming significantly cheaper and more scalable as more favourable materials are found.

### 1.1.2. Problem

By modelling data from known materials, this report will attempt to identify parameters of significance leading to higher values of Tc. This may provide some clues for the properties that researchers should look for in newly proposed materials. There are some research precedents investigating new materials using statistical methods, with some success [4]. Methods carried out in prior research include linear regression, as well as more complex machine learning techniques like artificial neural networks and gradient-boosting decision trees [5].

### 1.1.3. Challenges

One recent well-known example which speaks to the difficulty of discovering these materials was proposed by researchers [6] at Korea University in July 2023. This material, a grey-black, polycrystalline compound, identified as a copper-doped lead-oxyapatite and named LK-99 by the team which discovered it, was claimed to exhibit superconducting properties at room temperature and ambient pressure. While the results were never replicated, the months following LK-99’s publicity saw a flurry of media reporting on the great significance of what this discovery would mean for new technologies [7].

Challenges specific to discovering new materials through linear regression include:

1. **Non-linear relationships**. Superconductivity is governed by complex physical phenomena that often exhibit non-linear relationships. Linear regression assumes a linear relationship between variables, which may not capture these complexities accurately.

2. **High dimensionality**. Superconducting materials are characterized by numerous properties, such as first ionization energy, atomic radius, electron affinity, and fusion heat. This high-dimensional data must be handled carefully to avoid overfitting.

3. **Limited data availability**. Experimental data on superconducting materials is scarce and often noisy. Linear regression models require a large amount of data to produce reliable predictions, and limited data can lead to inaccurate models.

## 1.2. OBJECTIVES

### 1.2.1. Overview

The overall intent of the project is to create a regression model to predict the Critical Temperature (Tc) of different materials. An accurate regression model to predict Tc can be used to identify which factors lead to a higher Tc. However, great care must be taken if looking for Tc values above the range of values used in creating our model.

### 1.2.2. Goals & Research Questions

What combination of factors are the most accurate for predicting the Critical Temperature (Tc) of a given material?

What factors should a material scientist focus on when looking for new superconductor materials?

Can we use the measured properties of existing materials to accurately predict a new (hypothetical) super-conductor material with higher Tc than currently existing materials?

# 2. METHODOLOGY

## 2.1. Data

```{r, echo=FALSE}
library(GGally)
library(ggplot2)
library(mctest)
library(olsrr)
library(lmtest)

plot_ggpairs <- function(data) {
  ggpairs(
    data,
    lower = list(
      continuous = wrap("smooth", method = "loess", color = "red"),
      combo = "facethist",
      discrete = "facetbar",
      na = "na"
    ),
    upper = list(
      continuous = "cor"
    ),
    diag = list(
      continuous = "densityDiag"
    ),
    progress = FALSE
  ) +
    theme_bw()
}
```

```{r, echo=FALSE}
superconductivity = read.csv("../data/train.csv")
head(superconductivity)
```

```{r, echo=FALSE}
summary(superconductivity)
```

```{r, echo=FALSE}
str(superconductivity)
```

## 2.2. Approach
## 2.3. Workflow

```{r, echo=FALSE}
temp_model_additive = lm(critical_temp~., data=superconductivity)
summary(temp_model_additive)
```

All non-significant ($\alpha$ = 0.01) variables will be removed manually:

```{r, echo=FALSE}
temp_model_additive_reduced_1 = lm(critical_temp~.-wtd_range_Density, data=superconductivity)
summary(temp_model_additive_reduced_1)
```

```{r, echo=FALSE}
temp_model_additive_reduced_2 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density,
                data=superconductivity)
summary(temp_model_additive_reduced_2)
```

```{r, echo=FALSE}
temp_model_additive_reduced_3 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity, data=superconductivity)
summary(temp_model_additive_reduced_3)
```

```{r, echo=FALSE}
temp_model_additive_reduced_4 = lm(critical_temp~.-wtd_range_Density
                -wtd_mean_Density-wtd_std_ThermalConductivity
                -wtd_entropy_ThermalConductivity, data=superconductivity)
summary(temp_model_additive_reduced_4)
```

```{r, echo=FALSE}
temp_model_additive_reduced_5 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius, data=superconductivity)
summary(temp_model_additive_reduced_5)
```

```{r, echo=FALSE}
temp_model_additive_reduced_6 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass, data=superconductivity)
summary(temp_model_additive_reduced_6)
```

```{r, echo=FALSE}
temp_model_additive_reduced_7 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass,
                data=superconductivity)
summary(temp_model_additive_reduced_7)
```

```{r, echo=FALSE}
temp_model_additive_reduced_8 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence, data=superconductivity)
summary(temp_model_additive_reduced_8)
```

```{r, echo=FALSE}
temp_model_additive_reduced_9 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence-wtd_std_fie, data=superconductivity)
summary(temp_model_additive_reduced_9)
```

```{r, echo=FALSE}
temp_model_additive_reduced_10 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass
                -wtd_range_atomic_mass-wtd_range_Valence
                -wtd_std_fie-wtd_std_atomic_mass, data=superconductivity)
summary(temp_model_additive_reduced_10)
```

```{r, echo=FALSE}
temp_model_additive_reduced_11 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence-wtd_std_fie-wtd_std_atomic_mass
                -entropy_ElectronAffinity, data=superconductivity)
summary(temp_model_additive_reduced_11)
```

```{r, echo=FALSE}
temp_model_additive_reduced_12 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence-wtd_std_fie-wtd_std_atomic_mass
                -entropy_ElectronAffinity-std_FusionHeat, data=superconductivity)
summary(temp_model_additive_reduced_12)
```

```{r, echo=FALSE}
temp_model_additive_reduced_13 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence-wtd_std_fie-wtd_std_atomic_mass
                -entropy_ElectronAffinity-std_FusionHeat-mean_Valence, 
                data=superconductivity)
summary(temp_model_additive_reduced_13)
```

```{r, echo=FALSE}
temp_model_additive_reduced_14 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence-wtd_std_fie-wtd_std_atomic_mass
                -entropy_ElectronAffinity-std_FusionHeat-mean_Valence
                -std_Valence, data=superconductivity)
summary(temp_model_additive_reduced_14)
```

The following is the model including all significant variables:

```{r, echo=FALSE}
temp_model_additive_reduced_15 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence-wtd_std_fie-wtd_std_atomic_mass-entropy_ElectronAffinity
                -std_FusionHeat-mean_Valence-std_Valence-wtd_mean_Valence,
                data=superconductivity)
summary(temp_model_additive_reduced_15)
```

To identify correlations between predictor variables (potential multicollinearity):

```{r, echo=FALSE}
atomic_mass = superconductivity[, c("mean_atomic_mass", "wtd_mean_atomic_mass",
                                    "gmean_atomic_mass", "wtd_gmean_atomic_mass",
                                    "entropy_atomic_mass", "range_atomic_mass",
                                    "std_atomic_mass")]
plot_ggpairs(atomic_mass)
```

```{r, echo=FALSE}
fie = superconductivity[, c("mean_fie", "wtd_mean_fie", "gmean_fie", "wtd_gmean_fie",
                            "entropy_fie", "wtd_entropy_fie", "range_fie",
                            "wtd_range_fie", "std_fie")]
plot_ggpairs(fie)
```

```{r, echo=FALSE}
atomic_radius = superconductivity[, c("mean_atomic_radius", "wtd_mean_atomic_radius",
                                      "wtd_gmean_atomic_radius", "entropy_atomic_radius",
                                      "wtd_entropy_atomic_radius", "range_atomic_radius",
                                      "wtd_range_atomic_radius", "std_atomic_radius",
                                      "wtd_std_atomic_radius" )]
plot_ggpairs(atomic_radius)
```

```{r, echo=FALSE}
density = superconductivity[, c("mean_Density", "gmean_Density", "wtd_gmean_Density",
                                "entropy_Density", "wtd_entropy_Density",
                                "range_Density", "std_Density", "wtd_std_Density")]
plot_ggpairs(density)
```

```{r, echo=FALSE}
ElectronAffinity = superconductivity[, c("mean_ElectronAffinity", "wtd_mean_ElectronAffinity",
                                         "gmean_ElectronAffinity", "wtd_gmean_ElectronAffinity",
                                         "wtd_entropy_ElectronAffinity", "range_ElectronAffinity",
                                         "wtd_range_ElectronAffinity", "std_ElectronAffinity",
                                         "wtd_std_ElectronAffinity")]
plot_ggpairs(ElectronAffinity)
```

```{r, echo=FALSE}
FusionHeat = superconductivity[, c("mean_FusionHeat", "wtd_mean_FusionHeat",
                                   "gmean_FusionHeat", "wtd_gmean_FusionHeat",
                                   "entropy_FusionHeat", "wtd_entropy_FusionHeat",
                                   "range_FusionHeat", "wtd_range_FusionHeat",
                                   "wtd_std_FusionHeat")]
plot_ggpairs(FusionHeat)
```

```{r, echo=FALSE}
ThermalConductivity = superconductivity[, c("mean_ThermalConductivity",
                                            "wtd_mean_ThermalConductivity",
                                            "gmean_ThermalConductivity",
                                            "wtd_gmean_ThermalConductivity",
                                            "entropy_ThermalConductivity",
                                            "range_ThermalConductivity",
                                            "wtd_range_ThermalConductivity",
                                            "std_ThermalConductivity")]
plot_ggpairs(ThermalConductivity)
```

```{r, echo=FALSE}
Valence = superconductivity[, c("gmean_Valence", "wtd_gmean_Valence", "entropy_Valence",
                                "wtd_entropy_Valence", "range_Valence", "wtd_std_Valence")]
plot_ggpairs(Valence)
```

All highly correlated (> 0.9) variables will be removed:

```{r, echo=FALSE}
temp_model_additive_reduced_16 = lm(critical_temp~number_of_elements+mean_atomic_mass
                         +wtd_mean_atomic_mass+entropy_atomic_mass+range_atomic_mass
                         +mean_fie+wtd_mean_fie+entropy_fie+wtd_entropy_fie
                         +range_fie+wtd_range_fie+mean_atomic_radius
                         +wtd_mean_atomic_radius+entropy_atomic_radius
                         +range_atomic_radius+wtd_range_atomic_radius+mean_Density
                         +gmean_Density+entropy_Density+wtd_entropy_Density
                         +range_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity
                         +range_ElectronAffinity+wtd_range_ElectronAffinity
                         +wtd_std_ElectronAffinity+mean_FusionHeat+wtd_gmean_FusionHeat
                         +entropy_FusionHeat+wtd_entropy_FusionHeat+range_FusionHeat
                         +wtd_range_FusionHeat+mean_ThermalConductivity
                         +wtd_mean_ThermalConductivity+gmean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +range_ThermalConductivity+wtd_range_ThermalConductivity
                         +gmean_Valence+entropy_Valence+range_Valence+wtd_std_Valence,
                         data=superconductivity)
summary(temp_model_additive_reduced_16)
```

```{r, echo=FALSE}
temp_model_additive_reduced_17 = lm(critical_temp~number_of_elements+mean_atomic_mass
                         +wtd_mean_atomic_mass+entropy_atomic_mass+range_atomic_mass
                         +mean_fie+wtd_mean_fie+entropy_fie+wtd_entropy_fie+range_fie
                         +wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                         +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                         +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                         +range_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity
                         +range_ElectronAffinity+wtd_range_ElectronAffinity
                         +wtd_std_ElectronAffinity+wtd_gmean_FusionHeat+entropy_FusionHeat
                         +wtd_entropy_FusionHeat+range_FusionHeat+wtd_range_FusionHeat
                         +mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +gmean_ThermalConductivity+wtd_gmean_ThermalConductivity
                         +entropy_ThermalConductivity+range_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+entropy_Valence
                         +range_Valence+wtd_std_Valence, data=superconductivity)
summary(temp_model_additive_reduced_17)
```

```{r, echo=FALSE}
temp_model_additive_reduced_18 = lm(critical_temp~number_of_elements+mean_atomic_mass
                         +wtd_mean_atomic_mass+entropy_atomic_mass+range_atomic_mass
                         +mean_fie+wtd_mean_fie+entropy_fie+wtd_entropy_fie+range_fie
                         +wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                         +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                         +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                         +range_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity
                         +range_ElectronAffinity+wtd_range_ElectronAffinity
                         +wtd_std_ElectronAffinity+wtd_gmean_FusionHeat+entropy_FusionHeat
                         +wtd_entropy_FusionHeat+range_FusionHeat+wtd_range_FusionHeat
                         +mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +gmean_ThermalConductivity+wtd_gmean_ThermalConductivity
                         +entropy_ThermalConductivity+wtd_range_ThermalConductivity
                         +gmean_Valence+ entropy_Valence+range_Valence+wtd_std_Valence,
                         data=superconductivity)
summary(temp_model_additive_reduced_18)
```

```{r, echo=FALSE}
temp_model_additive_reduced_19 = lm(critical_temp~number_of_elements+mean_atomic_mass
                         +wtd_mean_atomic_mass+entropy_atomic_mass+range_atomic_mass
                         +mean_fie+wtd_mean_fie+entropy_fie+wtd_entropy_fie+range_fie
                         +wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                         +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                         +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                         +range_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity
                         +range_ElectronAffinity+wtd_range_ElectronAffinity
                         +wtd_std_ElectronAffinity+wtd_gmean_FusionHeat+entropy_FusionHeat
                         +wtd_entropy_FusionHeat+range_FusionHeat+wtd_range_FusionHeat
                         +mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +gmean_ThermalConductivity+wtd_gmean_ThermalConductivity
                         +entropy_ThermalConductivity+wtd_range_ThermalConductivity
                         +gmean_Valence+range_Valence+wtd_std_Valence, data=superconductivity)
summary(temp_model_additive_reduced_19)
```

```{r, echo=FALSE}
temp_model_additive_reduced_20 = lm(critical_temp~number_of_elements+mean_atomic_mass
                         +wtd_mean_atomic_mass+entropy_atomic_mass+range_atomic_mass
                         +mean_fie+wtd_mean_fie+entropy_fie+wtd_entropy_fie+range_fie
                         +wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                         +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                         +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                         +mean_ElectronAffinity+wtd_mean_ElectronAffinity+gmean_ElectronAffinity
                         +wtd_entropy_ElectronAffinity+range_ElectronAffinity
                         +wtd_range_ElectronAffinity+wtd_std_ElectronAffinity
                         +wtd_gmean_FusionHeat+entropy_FusionHeat+wtd_entropy_FusionHeat
                         +range_FusionHeat+wtd_range_FusionHeat+mean_ThermalConductivity
                         +wtd_mean_ThermalConductivity+gmean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+range_Valence
                         +wtd_std_Valence, data=superconductivity)
summary(temp_model_additive_reduced_20)
```

```{r, echo=FALSE}
temp_model_additive_reduced_21 = lm(critical_temp~number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                         +entropy_atomic_mass+range_atomic_mass+mean_fie+wtd_mean_fie
                         +entropy_fie+wtd_entropy_fie+range_fie+wtd_range_fie+mean_atomic_radius
                         +wtd_mean_atomic_radius+entropy_atomic_radius+range_atomic_radius
                         +wtd_range_atomic_radius+mean_Density+gmean_Density+entropy_Density
                         +wtd_entropy_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity+range_ElectronAffinity
                         +wtd_range_ElectronAffinity+wtd_std_ElectronAffinity+wtd_gmean_FusionHeat
                         +entropy_FusionHeat+wtd_entropy_FusionHeat+range_FusionHeat
                         +wtd_range_FusionHeat+mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+range_Valence+wtd_std_Valence,
                         data=superconductivity)
summary(temp_model_additive_reduced_21)
```

```{r, echo=FALSE}
temp_model_additive_reduced_22 = lm(critical_temp~number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                         +entropy_atomic_mass+range_atomic_mass+wtd_mean_fie+entropy_fie
                         +wtd_entropy_fie+range_fie+wtd_range_fie+mean_atomic_radius
                         +wtd_mean_atomic_radius+entropy_atomic_radius+range_atomic_radius
                         +wtd_range_atomic_radius+mean_Density+gmean_Density+entropy_Density
                         +wtd_entropy_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity+range_ElectronAffinity
                         +wtd_range_ElectronAffinity+wtd_std_ElectronAffinity+wtd_gmean_FusionHeat
                         +entropy_FusionHeat+wtd_entropy_FusionHeat+range_FusionHeat
                         +wtd_range_FusionHeat+mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+range_Valence+wtd_std_Valence,
                         data=superconductivity)
summary(temp_model_additive_reduced_22)
```

```{r, echo=FALSE}
temp_model_additive_reduced_23 = lm(critical_temp~number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                         +entropy_atomic_mass+range_atomic_mass+wtd_mean_fie+entropy_fie
                         +wtd_entropy_fie+wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                         +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                         +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                         +mean_ElectronAffinity+wtd_mean_ElectronAffinity+gmean_ElectronAffinity
                         +wtd_entropy_ElectronAffinity+range_ElectronAffinity+wtd_range_ElectronAffinity
                         +wtd_std_ElectronAffinity+wtd_gmean_FusionHeat+entropy_FusionHeat
                         +wtd_entropy_FusionHeat+range_FusionHeat+wtd_range_FusionHeat
                         +mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+range_Valence+wtd_std_Valence,
                         data=superconductivity)
summary(temp_model_additive_reduced_23)
```

```{r, echo=FALSE}
temp_model_additive_reduced_24 = lm(critical_temp~number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                         +entropy_atomic_mass+range_atomic_mass+wtd_mean_fie+entropy_fie
                         +wtd_entropy_fie+range_fie+wtd_range_fie+mean_atomic_radius
                         +wtd_mean_atomic_radius+entropy_atomic_radius+range_atomic_radius
                         +wtd_range_atomic_radius+mean_Density+gmean_Density+entropy_Density
                         +wtd_entropy_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity+range_ElectronAffinity
                         +wtd_range_ElectronAffinity+wtd_gmean_FusionHeat+entropy_FusionHeat
                         +wtd_entropy_FusionHeat+range_FusionHeat+wtd_range_FusionHeat
                         +mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+range_Valence
                         +wtd_std_Valence, data=superconductivity)
summary(temp_model_additive_reduced_24)
```

```{r, echo=FALSE}
temp_model_additive_reduced_25 = lm(critical_temp~number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                         +entropy_atomic_mass+range_atomic_mass+wtd_mean_fie+entropy_fie
                         +wtd_entropy_fie+wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                         +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                         +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                         +mean_ElectronAffinity+wtd_mean_ElectronAffinity+gmean_ElectronAffinity
                         +wtd_entropy_ElectronAffinity+range_ElectronAffinity+wtd_range_ElectronAffinity
                         +wtd_gmean_FusionHeat+entropy_FusionHeat+wtd_entropy_FusionHeat+range_FusionHeat
                         +wtd_range_FusionHeat+mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+range_Valence+wtd_std_Valence,
                         data=superconductivity)
summary(temp_model_additive_reduced_25)
```

```{r, echo=FALSE}
temp_model_additive_reduced_26 = lm(critical_temp~number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                          +entropy_atomic_mass+range_atomic_mass+wtd_mean_fie+entropy_fie
                          +wtd_entropy_fie+wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                          +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                          +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                          +mean_ElectronAffinity+wtd_mean_ElectronAffinity+gmean_ElectronAffinity
                          +wtd_entropy_ElectronAffinity+range_ElectronAffinity+wtd_range_ElectronAffinity
                          +wtd_gmean_FusionHeat+entropy_FusionHeat+wtd_entropy_FusionHeat
                          +range_FusionHeat+wtd_range_FusionHeat+mean_ThermalConductivity
                          +wtd_mean_ThermalConductivity+wtd_gmean_ThermalConductivity
                          +entropy_ThermalConductivity+wtd_range_ThermalConductivity
                          +range_Valence+wtd_std_Valence, data=superconductivity)
summary(temp_model_additive_reduced_26)
```

```{r, echo=FALSE}
imcdiag(temp_model_additive_reduced_26, method="VIF")
```

```{r, echo=FALSE}
reduced_data_part_1 = superconductivity[, c("number_of_elements", "mean_atomic_mass",
                                            "wtd_mean_atomic_mass", "entropy_atomic_mass",
                                            "wtd_mean_fie", "entropy_fie",
                                            "wtd_entropy_fie", "wtd_range_fie")]
plot_ggpairs(reduced_data_part_1)
```

```{r, echo=FALSE}
reduced_data_part_2 = superconductivity[, c("wtd_mean_atomic_radius", "entropy_atomic_radius",
                                            "range_atomic_radius", "mean_Density",
                                            "gmean_Density", "entropy_Density",
                                            "wtd_entropy_Density")]
plot_ggpairs(reduced_data_part_2)
```

```{r, echo=FALSE}
reduced_data_part_3 = superconductivity[, c("mean_ElectronAffinity", "wtd_mean_ElectronAffinity",
                                            "gmean_ElectronAffinity", "wtd_entropy_ElectronAffinity",
                                            "wtd_range_ElectronAffinity", "entropy_FusionHeat",
                                            "wtd_entropy_FusionHeat", "wtd_mean_ThermalConductivity",
                                            "wtd_range_ThermalConductivity")]
plot_ggpairs(reduced_data_part_3)
```

```{r, echo=FALSE}
temp_model_additive_reduced_27 = lm(critical_temp ~ number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
             +wtd_mean_fie+wtd_entropy_fie+wtd_range_fie+wtd_mean_atomic_radius
             +entropy_atomic_radius+range_atomic_radius+mean_Density+wtd_entropy_Density
             +mean_ElectronAffinity+wtd_mean_ElectronAffinity+wtd_entropy_ElectronAffinity
             +wtd_range_ElectronAffinity+entropy_FusionHeat+wtd_mean_ThermalConductivity,
             data=superconductivity)
summary(temp_model_additive_reduced_27)
```

```{r, echo=FALSE}
imcdiag(temp_model_additive_reduced_27, method="VIF")
```

```{r, echo=FALSE}
reduced_data_part_4 = superconductivity[, c("number_of_elements", "wtd_mean_fie",
                                            "wtd_entropy_fie", "wtd_range_fie",
                                            "entropy_atomic_radius", "wtd_mean_ElectronAffinity",
                                            "wtd_range_ElectronAffinity", "entropy_FusionHeat")]
plot_ggpairs(reduced_data_part_4)
```

```{r, echo=FALSE}
temp_model_additive_reduced_28 = lm(critical_temp ~ number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
             +wtd_mean_fie+wtd_entropy_fie+wtd_range_fie+wtd_mean_atomic_radius
             +range_atomic_radius+mean_Density+wtd_entropy_Density+mean_ElectronAffinity
             +wtd_mean_ElectronAffinity+wtd_entropy_ElectronAffinity+wtd_mean_ThermalConductivity,
             data=superconductivity)
summary(temp_model_additive_reduced_28)
```

```{r, echo=FALSE}
final_model_additive = lm(critical_temp ~ number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
             +wtd_mean_fie+wtd_entropy_fie+wtd_mean_atomic_radius+range_atomic_radius
             +mean_Density+wtd_entropy_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
             +wtd_entropy_ElectronAffinity+wtd_mean_ThermalConductivity, data=superconductivity)
summary(final_model_additive)
```

```{r, echo=FALSE}
imcdiag(final_model_additive, method="VIF")
```

According to the output, the predictors are not affected by multicollinearity.

The model will be expanded to include interaction terms:

```{r, echo=FALSE}
temp_model_int = lm(critical_temp ~ (number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                                  +wtd_mean_fie+wtd_entropy_fie+wtd_mean_atomic_radius
                                  +range_atomic_radius+mean_Density+wtd_entropy_Density
                                  +mean_ElectronAffinity+wtd_mean_ElectronAffinity
                                  +wtd_entropy_ElectronAffinity+wtd_mean_ThermalConductivity)^2,
                 data=superconductivity)
summary(temp_model_int)
```

Non-significant variables will be removed using a forward selection approach:

```{r, echo=FALSE}
temp_model_int_reduced_1 = ols_step_forward_p(temp_model_int, p_val=0.01, details=FALSE)
summary(temp_model_int_reduced_1$model)
```

```{r, echo=FALSE}
temp_model_int_reduced_2 = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                     +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                     +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density
                     +wtd_mean_atomic_mass+mean_ElectronAffinity+mean_Density
                     +number_of_elements+wtd_entropy_fie+range_atomic_radius
                     +wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                     +range_atomic_radius:wtd_entropy_Density
                     +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                     +range_atomic_radius:wtd_mean_ElectronAffinity
                     +wtd_mean_fie:wtd_mean_ThermalConductivity
                     +number_of_elements:wtd_mean_atomic_mass
                     +range_atomic_radius:mean_Density+mean_atomic_mass:range_atomic_radius
                     +wtd_entropy_fie:wtd_mean_atomic_radius
                     +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                     +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                     +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                     +number_of_elements:wtd_mean_ThermalConductivity
                     +range_atomic_radius:mean_ElectronAffinity
                     +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                     +wtd_mean_atomic_radius:range_atomic_radius
                     +number_of_elements:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                     +number_of_elements:wtd_mean_ElectronAffinity
                     +number_of_elements:mean_ElectronAffinity+wtd_mean_atomic_mass:wtd_entropy_fie
                     +mean_atomic_mass:wtd_mean_fie+mean_atomic_mass:wtd_mean_atomic_radius
                     +wtd_mean_fie:mean_Density+range_atomic_radius:wtd_entropy_ElectronAffinity
                     +mean_atomic_mass:wtd_entropy_Density+wtd_entropy_Density:wtd_mean_ElectronAffinity
                     +wtd_entropy_fie:wtd_mean_ThermalConductivity+wtd_mean_fie:wtd_mean_atomic_radius
                     +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity+mean_atomic_mass:wtd_mean_ElectronAffinity
                     +mean_Density:wtd_mean_ElectronAffinity+wtd_mean_atomic_radius:mean_ElectronAffinity
                     +wtd_mean_atomic_mass:range_atomic_radius+wtd_entropy_Density:wtd_mean_ThermalConductivity
                     +mean_Density:wtd_mean_ThermalConductivity+mean_atomic_mass:wtd_mean_ThermalConductivity
                     +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                     +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                     +number_of_elements:wtd_entropy_ElectronAffinity+number_of_elements:wtd_entropy_fie
                     +wtd_mean_atomic_mass:wtd_entropy_Density+wtd_mean_atomic_radius:wtd_entropy_Density
                     +mean_ElectronAffinity:wtd_mean_ElectronAffinity+wtd_mean_fie:mean_ElectronAffinity
                     +number_of_elements:mean_Density+wtd_entropy_fie:mean_Density
                     +mean_Density:wtd_entropy_Density+wtd_mean_fie:wtd_entropy_ElectronAffinity
                     +number_of_elements:wtd_mean_fie+wtd_mean_fie:wtd_mean_ElectronAffinity
                     +wtd_entropy_fie:wtd_entropy_ElectronAffinity+wtd_entropy_fie:wtd_entropy_Density
                     +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_int_reduced_2)
```

The remaining non-significant ($\alpha$ = 0.01) variables will be removed manually:

```{r, echo=FALSE}
temp_model_int_reduced_3 = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                     +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                     +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density
                     +wtd_mean_atomic_mass+mean_ElectronAffinity+mean_Density+number_of_elements
                     +wtd_entropy_fie+range_atomic_radius+wtd_mean_ThermalConductivity
                     +wtd_mean_fie:range_atomic_radius+range_atomic_radius:wtd_entropy_Density
                     +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                     +range_atomic_radius:wtd_mean_ElectronAffinity
                     +wtd_mean_fie:wtd_mean_ThermalConductivity
                     +number_of_elements:wtd_mean_atomic_mass+range_atomic_radius:mean_Density
                     +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                     +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                     +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                     +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                     +number_of_elements:wtd_mean_ThermalConductivity
                     +range_atomic_radius:mean_ElectronAffinity+mean_atomic_mass:wtd_entropy_fie
                     +mean_atomic_mass:wtd_entropy_ElectronAffinity+wtd_mean_atomic_radius:range_atomic_radius
                     +number_of_elements:wtd_mean_atomic_radius+number_of_elements:wtd_mean_ElectronAffinity
                     +number_of_elements:mean_ElectronAffinity+wtd_mean_atomic_mass:wtd_entropy_fie
                     +mean_atomic_mass:wtd_mean_fie+mean_atomic_mass:wtd_mean_atomic_radius
                     +wtd_mean_fie:mean_Density+range_atomic_radius:wtd_entropy_ElectronAffinity
                     +mean_atomic_mass:wtd_entropy_Density+wtd_entropy_Density:wtd_mean_ElectronAffinity
                     +wtd_entropy_fie:wtd_mean_ThermalConductivity+wtd_mean_fie:wtd_mean_atomic_radius
                     +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity+mean_atomic_mass:wtd_mean_ElectronAffinity
                     +mean_Density:wtd_mean_ElectronAffinity+wtd_mean_atomic_radius:mean_ElectronAffinity
                     +wtd_mean_atomic_mass:range_atomic_radius+wtd_entropy_Density:wtd_mean_ThermalConductivity
                     +mean_Density:wtd_mean_ThermalConductivity+mean_atomic_mass:wtd_mean_ThermalConductivity
                     +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                     +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                     +number_of_elements:wtd_entropy_ElectronAffinity+number_of_elements:wtd_entropy_fie
                     +wtd_mean_atomic_mass:wtd_entropy_Density+wtd_mean_atomic_radius:wtd_entropy_Density
                     +mean_ElectronAffinity:wtd_mean_ElectronAffinity+wtd_mean_fie:mean_ElectronAffinity
                     +number_of_elements:mean_Density+wtd_entropy_fie:mean_Density
                     +mean_Density:wtd_entropy_Density+wtd_mean_fie:wtd_entropy_ElectronAffinity
                     +number_of_elements:wtd_mean_fie+wtd_mean_fie:wtd_mean_ElectronAffinity
                     +wtd_entropy_fie:wtd_entropy_ElectronAffinity+wtd_entropy_fie:wtd_entropy_Density
                     +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_int_reduced_3)
```

```{r, echo=FALSE}
temp_model_int_reduced_4 = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius
                 +range_atomic_radius:wtd_entropy_ElectronAffinity+mean_atomic_mass:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity+mean_Density:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_radius:wtd_entropy_Density
                 +wtd_mean_fie:mean_ElectronAffinity
                 +mean_Density:wtd_entropy_Density+wtd_mean_fie:wtd_entropy_ElectronAffinity
                 +number_of_elements:wtd_mean_fie+wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_int_reduced_4)
```

```{r, echo=FALSE}
temp_model_int_reduced_5 = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius
                 +range_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity+mean_Density:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_radius:wtd_entropy_Density
                 +wtd_mean_fie:mean_ElectronAffinity
                 +mean_Density:wtd_entropy_Density+wtd_mean_fie:wtd_entropy_ElectronAffinity
                 +number_of_elements:wtd_mean_fie+wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_int_reduced_5)
```

```{r, echo=FALSE}
temp_model_int_reduced_6 = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius
                 +range_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity+mean_Density:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_fie:mean_ElectronAffinity
                 +mean_Density:wtd_entropy_Density+wtd_mean_fie:wtd_entropy_ElectronAffinity
                 +number_of_elements:wtd_mean_fie+wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_int_reduced_6)
```

```{r, echo=FALSE}
temp_model_int_reduced_7 = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius
                 +range_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_fie:mean_ElectronAffinity
                 +mean_Density:wtd_entropy_Density+wtd_mean_fie:wtd_entropy_ElectronAffinity
                 +number_of_elements:wtd_mean_fie+wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_int_reduced_7)
```

```{r, echo=FALSE}
temp_model_int_reduced_8 = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius
                 +range_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_fie:mean_ElectronAffinity
                 +mean_Density:wtd_entropy_Density+wtd_mean_fie:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_int_reduced_8)
```

```{r, echo=FALSE}
temp_model_int_reduced_9 = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_fie:mean_ElectronAffinity
                 +mean_Density:wtd_entropy_Density+wtd_mean_fie:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_int_reduced_9)
```

```{r, echo=FALSE}
temp_model_int_reduced_10 = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_fie:mean_ElectronAffinity
                 +mean_Density:wtd_entropy_Density
                 +wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_int_reduced_10)
```

```{r, echo=FALSE}
temp_model_int_reduced_11 = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_fie:mean_ElectronAffinity
                 +mean_Density:wtd_entropy_Density
                 +wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_int_reduced_11)
```

```{r, echo=FALSE}
final_int_model = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_fie:mean_ElectronAffinity
                 +mean_Density:wtd_entropy_Density
                 +wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(final_int_model)
```

```{r, echo=FALSE}
temp_int_drop = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_fie:mean_ElectronAffinity
                 +mean_Density:wtd_entropy_Density
                 +wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(final_int_model)
```








### Linearity Assumption

```{r, echo=FALSE}
ggplot(final_int_model, aes(x=.fitted, y=.resid)) + geom_point() + geom_smooth() +
  geom_hline(yintercept=0) 
```

```{r, echo=FALSE}
final_data = superconductivity[, c("critical_temp", "wtd_mean_ElectronAffinity", "wtd_mean_atomic_radius",
                                   "mean_atomic_mass", "wtd_mean_fie", "wtd_entropy_ElectronAffinity",
                                   "wtd_entropy_Density", "wtd_mean_atomic_mass",
                                   "mean_ElectronAffinity", "mean_Density", "number_of_elements",
                                   "wtd_entropy_fie", "range_atomic_radius", "wtd_mean_ThermalConductivity")]
plot_ggpairs(final_data)
```

```{r, echo=FALSE}
temp_model_linearity_ass = lm(log(critical_temp) ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_fie:mean_ElectronAffinity
                 +mean_Density:wtd_entropy_Density
                 +wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_linearity_ass)
```

```{r, echo=FALSE}
ggplot(temp_model_linearity_ass, aes(x=.fitted, y=.resid)) + geom_point() + geom_smooth() +
  geom_hline(yintercept=0) + ggtitle("Residual plot: Residual vs Fitted values")
```

```{r, echo=FALSE}
superconductivity$log_critical_temp <- log(superconductivity$critical_temp)

temp_model_linearity_ass_1= lm(log_critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_fie:mean_ElectronAffinity
                 +mean_Density:wtd_entropy_Density
                 +wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_linearity_ass_1)
```

```{r, echo=FALSE}
temp_model_linearity_ass_reduced_1 <- ols_step_forward_p(temp_model_linearity_ass_1,
                                                         p_val = 0.01, details = FALSE)
summary(temp_model_linearity_ass_reduced_1$model)
```

```{r, echo=FALSE}
final_reduced =  lm(log_critical_temp ~ range_atomic_radius  + wtd_mean_ElectronAffinity  +wtd_mean_ThermalConductivity+ 
wtd_mean_fie +wtd_entropy_Density  +mean_atomic_mass+ wtd_entropy_fie + 
wtd_mean_atomic_radius +mean_ElectronAffinity + wtd_entropy_ElectronAffinity +  
wtd_mean_atomic_mass + number_of_elements  +mean_Density + 
range_atomic_radius:wtd_mean_ThermalConductivity  + 
range_atomic_radius:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_atomic_radius + 
wtd_mean_ThermalConductivity:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity + 
range_atomic_radius:wtd_entropy_Density + 
wtd_entropy_Density:wtd_entropy_ElectronAffinity  + 
wtd_mean_ElectronAffinity:number_of_elements + 
range_atomic_radius:wtd_mean_atomic_mass + 
wtd_mean_ElectronAffinity:mean_atomic_mass + 
wtd_mean_fie:mean_atomic_mass + 
mean_atomic_mass:wtd_mean_atomic_radius + 
range_atomic_radius:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_Density + 
wtd_entropy_Density:mean_Density + 
wtd_mean_ThermalConductivity:wtd_entropy_ElectronAffinity + 
wtd_entropy_fie:wtd_mean_atomic_mass + 
mean_atomic_mass:wtd_entropy_fie+ 
wtd_entropy_Density:wtd_entropy_fie + 
wtd_mean_ElectronAffinity:wtd_entropy_Density + 
wtd_entropy_fie:mean_ElectronAffinity + 
mean_ElectronAffinity:number_of_elements+ 
wtd_mean_atomic_radius:number_of_elements+ 
wtd_entropy_fie:wtd_mean_atomic_radius+ 
wtd_mean_ThermalConductivity:number_of_elements + 
wtd_mean_ElectronAffinity:wtd_mean_fie, data = superconductivity, ,na.action=na.exclude)
summary(final_reduced)
```

### Independence Assumption

The independence assumption in regression means that residuals should not influence each other. Since our data is not time-series and there is no natural order or dependency between observations, this assumption is likely satisfied. Meeting this assumption ensures that the results are reliable and not affected by biased standard errors. ++++++++++++++++++++

### Equal Variance Assumption

```{r, echo=FALSE}
ggplot(final_reduced, aes(x=.fitted, y=.resid)) + geom_point() + geom_smooth() +
  geom_hline(yintercept=0) + ggtitle("Residual plot: Residual vs Fitted values")
```

```{r, echo=FALSE}
ggplot(final_reduced, aes(x=.fitted, y=sqrt(abs(.stdresid)))) + geom_point() +
  geom_smooth() + geom_hline(yintercept=0) +
  ggtitle("Scale-Location plot: Standardized Residual vs Fitted values")
```

```{r, echo=FALSE}
bptest(final_reduced)
```

We reject the null hypothesis (p-value < 0.05), concluding that heteroscedasticity exists.

```{r, echo=FALSE}
data = superconductivity[,c("log_critical_temp" , "range_atomic_radius"  , "wtd_mean_ElectronAffinity"  , "wtd_mean_ThermalConductivity", "wtd_mean_fie", "wtd_entropy_Density"  , "mean_atomic_mass" , "wtd_entropy_fie", "wtd_mean_atomic_radius", "mean_ElectronAffinity", "wtd_entropy_ElectronAffinity", "wtd_mean_atomic_mass", "number_of_elements", "mean_Density")]
plot_ggpairs(data)
```

```{r, echo=FALSE}
wt <- 1 / fitted(final_reduced)^0.01

weighted_model =  lm(log_critical_temp ~ range_atomic_radius  + wtd_mean_ElectronAffinity  +wtd_mean_ThermalConductivity+ 
wtd_mean_fie +wtd_entropy_Density  +mean_atomic_mass+ wtd_entropy_fie + 
wtd_mean_atomic_radius +mean_ElectronAffinity + wtd_entropy_ElectronAffinity +  
wtd_mean_atomic_mass + number_of_elements  +mean_Density + 
range_atomic_radius:wtd_mean_ThermalConductivity  + 
range_atomic_radius:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_atomic_radius + 
wtd_mean_ThermalConductivity:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity + 
range_atomic_radius:wtd_entropy_Density + 
wtd_entropy_Density:wtd_entropy_ElectronAffinity  + 
wtd_mean_ElectronAffinity:number_of_elements + 
range_atomic_radius:wtd_mean_atomic_mass + 
wtd_mean_ElectronAffinity:mean_atomic_mass + 
wtd_mean_fie:mean_atomic_mass + 
mean_atomic_mass:wtd_mean_atomic_radius + 
range_atomic_radius:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_Density + 
wtd_entropy_Density:mean_Density + 
wtd_mean_ThermalConductivity:wtd_entropy_ElectronAffinity + 
wtd_entropy_fie:wtd_mean_atomic_mass + 
mean_atomic_mass:wtd_entropy_fie+ 
wtd_entropy_Density:wtd_entropy_fie + 
wtd_mean_ElectronAffinity:wtd_entropy_Density + 
wtd_entropy_fie:mean_ElectronAffinity + 
mean_ElectronAffinity:number_of_elements+ 
wtd_mean_atomic_radius:number_of_elements+ 
wtd_entropy_fie:wtd_mean_atomic_radius+ 
wtd_mean_ThermalConductivity:number_of_elements + 
wtd_mean_ElectronAffinity:wtd_mean_fie, data = superconductivity, weights = wt)
summary(weighted_model)
```

```{r, echo=FALSE}
weighted_model2 = lm(log_critical_temp ~ range_atomic_radius  + wtd_mean_ElectronAffinity  +wtd_mean_ThermalConductivity+ 
wtd_mean_fie +wtd_entropy_Density  +mean_atomic_mass+ wtd_entropy_fie + 
wtd_mean_atomic_radius +mean_ElectronAffinity + wtd_entropy_ElectronAffinity +  
wtd_mean_atomic_mass + number_of_elements  +mean_Density + 
range_atomic_radius:wtd_mean_ThermalConductivity  + 
range_atomic_radius:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_atomic_radius + 
wtd_mean_ThermalConductivity:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity + 
range_atomic_radius:wtd_entropy_Density + 
wtd_entropy_Density:wtd_entropy_ElectronAffinity  + 
wtd_mean_ElectronAffinity:number_of_elements + 
range_atomic_radius:wtd_mean_atomic_mass + 
wtd_mean_ElectronAffinity:mean_atomic_mass + 
wtd_mean_fie:mean_atomic_mass + 
mean_atomic_mass:wtd_mean_atomic_radius + 
range_atomic_radius:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_Density + 
wtd_entropy_Density:mean_Density + 
wtd_mean_ThermalConductivity:wtd_entropy_ElectronAffinity + 
wtd_entropy_fie:wtd_mean_atomic_mass + 
mean_atomic_mass:wtd_entropy_fie+
wtd_mean_ElectronAffinity:wtd_entropy_Density + 
wtd_entropy_fie:mean_ElectronAffinity + 
mean_ElectronAffinity:number_of_elements+ 
wtd_mean_atomic_radius:number_of_elements+ 
wtd_entropy_fie:wtd_mean_atomic_radius+ 
wtd_mean_ThermalConductivity:number_of_elements + 
wtd_mean_ElectronAffinity:wtd_mean_fie, data = superconductivity, weights = wt)

summary(weighted_model2)
```

```{r, echo=FALSE}
weighted_model3 = lm(log_critical_temp ~ range_atomic_radius  + wtd_mean_ElectronAffinity  +wtd_mean_ThermalConductivity+ 
wtd_mean_fie +wtd_entropy_Density  +mean_atomic_mass+ wtd_entropy_fie + 
wtd_mean_atomic_radius +mean_ElectronAffinity + wtd_entropy_ElectronAffinity +  
wtd_mean_atomic_mass + number_of_elements  +mean_Density + 
range_atomic_radius:wtd_mean_ThermalConductivity  + 
range_atomic_radius:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_atomic_radius + 
wtd_mean_ThermalConductivity:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity + 
range_atomic_radius:wtd_entropy_Density + 
wtd_entropy_Density:wtd_entropy_ElectronAffinity  + 
wtd_mean_ElectronAffinity:number_of_elements + 
range_atomic_radius:wtd_mean_atomic_mass + 
wtd_mean_ElectronAffinity:mean_atomic_mass + 
wtd_mean_fie:mean_atomic_mass + 
mean_atomic_mass:wtd_mean_atomic_radius + 
range_atomic_radius:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_Density + 
wtd_mean_ThermalConductivity:wtd_entropy_ElectronAffinity + 
wtd_entropy_fie:wtd_mean_atomic_mass + 
mean_atomic_mass:wtd_entropy_fie+
wtd_mean_ElectronAffinity:wtd_entropy_Density + 
wtd_entropy_fie:mean_ElectronAffinity + 
mean_ElectronAffinity:number_of_elements+ 
wtd_mean_atomic_radius:number_of_elements+ 
wtd_entropy_fie:wtd_mean_atomic_radius+ 
wtd_mean_ThermalConductivity:number_of_elements + 
wtd_mean_ElectronAffinity:wtd_mean_fie, data = superconductivity, weights = wt)

summary(weighted_model3)
```

```{r, echo=FALSE}
weighted_model4 = lm(log_critical_temp ~ range_atomic_radius  + wtd_mean_ElectronAffinity  +wtd_mean_ThermalConductivity+ 
wtd_mean_fie +wtd_entropy_Density  +mean_atomic_mass+ wtd_entropy_fie + 
wtd_mean_atomic_radius +mean_ElectronAffinity + wtd_entropy_ElectronAffinity +  
wtd_mean_atomic_mass + number_of_elements  +mean_Density + 
range_atomic_radius:wtd_mean_ThermalConductivity  + 
range_atomic_radius:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_atomic_radius + 
wtd_mean_ThermalConductivity:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity + 
range_atomic_radius:wtd_entropy_Density + 
wtd_entropy_Density:wtd_entropy_ElectronAffinity  + 
wtd_mean_ElectronAffinity:number_of_elements + 
range_atomic_radius:wtd_mean_atomic_mass + 
wtd_mean_ElectronAffinity:mean_atomic_mass + 
wtd_mean_fie:mean_atomic_mass + 
mean_atomic_mass:wtd_mean_atomic_radius + 
range_atomic_radius:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_Density + 
wtd_entropy_fie:wtd_mean_atomic_mass + 
mean_atomic_mass:wtd_entropy_fie+
wtd_mean_ElectronAffinity:wtd_entropy_Density + 
wtd_entropy_fie:mean_ElectronAffinity + 
mean_ElectronAffinity:number_of_elements+ 
wtd_mean_atomic_radius:number_of_elements+ 
wtd_entropy_fie:wtd_mean_atomic_radius+ 
wtd_mean_ThermalConductivity:number_of_elements + 
wtd_mean_ElectronAffinity:wtd_mean_fie, data = superconductivity, weights = wt)

summary(weighted_model4)
```


```{r, echo=FALSE}
weighted_model5 = lm(log_critical_temp ~ range_atomic_radius  + wtd_mean_ElectronAffinity  +wtd_mean_ThermalConductivity+ 
wtd_mean_fie +wtd_entropy_Density  +mean_atomic_mass+ wtd_entropy_fie + 
wtd_mean_atomic_radius +mean_ElectronAffinity + wtd_entropy_ElectronAffinity +  
wtd_mean_atomic_mass + number_of_elements  +mean_Density + 
range_atomic_radius:wtd_mean_ThermalConductivity  + 
range_atomic_radius:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_atomic_radius + 
wtd_mean_ThermalConductivity:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity + 
range_atomic_radius:wtd_entropy_Density + 
wtd_entropy_Density:wtd_entropy_ElectronAffinity  + 
wtd_mean_ElectronAffinity:number_of_elements + 
range_atomic_radius:wtd_mean_atomic_mass + 
wtd_mean_ElectronAffinity:mean_atomic_mass + 
wtd_mean_fie:mean_atomic_mass + 
mean_atomic_mass:wtd_mean_atomic_radius + 
range_atomic_radius:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_Density + 
wtd_entropy_fie:wtd_mean_atomic_mass + 
mean_atomic_mass:wtd_entropy_fie+
wtd_mean_ElectronAffinity:wtd_entropy_Density + 
wtd_entropy_fie:mean_ElectronAffinity + 
mean_ElectronAffinity:number_of_elements+ 
wtd_mean_atomic_radius:number_of_elements+ 
wtd_entropy_fie:wtd_mean_atomic_radius+ 
wtd_mean_ElectronAffinity:wtd_mean_fie, data = superconductivity, weights = wt)

summary(weighted_model5)
```

```{r, echo=FALSE}
weighted_model6 = lm(log_critical_temp ~ range_atomic_radius  + wtd_mean_ElectronAffinity  +wtd_mean_ThermalConductivity+ 
wtd_mean_fie +wtd_entropy_Density  +mean_atomic_mass+ wtd_entropy_fie + 
wtd_mean_atomic_radius +mean_ElectronAffinity + wtd_entropy_ElectronAffinity +  
wtd_mean_atomic_mass + number_of_elements  +mean_Density + 
range_atomic_radius:wtd_mean_ThermalConductivity  + 
range_atomic_radius:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_atomic_radius + 
wtd_mean_ThermalConductivity:wtd_mean_fie + 
wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity + 
range_atomic_radius:wtd_entropy_Density + 
wtd_entropy_Density:wtd_entropy_ElectronAffinity  + 
wtd_mean_ElectronAffinity:number_of_elements + 
range_atomic_radius:wtd_mean_atomic_mass + 
wtd_mean_ElectronAffinity:mean_atomic_mass + 
wtd_mean_fie:mean_atomic_mass + 
mean_atomic_mass:wtd_mean_atomic_radius + 
range_atomic_radius:mean_atomic_mass + 
wtd_mean_ThermalConductivity:mean_atomic_mass + 
wtd_entropy_fie:wtd_mean_atomic_mass + 
mean_atomic_mass:wtd_entropy_fie+
wtd_mean_ElectronAffinity:wtd_entropy_Density + 
wtd_entropy_fie:mean_ElectronAffinity + 
mean_ElectronAffinity:number_of_elements+ 
wtd_mean_atomic_radius:number_of_elements+ 
wtd_entropy_fie:wtd_mean_atomic_radius+ 
wtd_mean_ElectronAffinity:wtd_mean_fie, data = superconductivity, weights = wt)

summary(weighted_model6)
```

```{r, echo=FALSE}
ggplot(weighted_model6, aes(x=.fitted, y=.resid)) + geom_point() + geom_smooth() +
  geom_hline(yintercept=0) + ggtitle("Residual plot: Residual vs Fitted values")
```

```{r, echo=FALSE}
ggplot(weighted_model6, aes(x=.fitted, y=sqrt(abs(.stdresid)))) + geom_point() +
  geom_smooth() + geom_hline(yintercept=0) +
  ggtitle("Scale-Location plot: Standardized Residual vs Fitted values")
```

```{r, echo=FALSE}
bptest(weighted_model6)
```

```{r, echo=FALSE}
hist(residuals(weighted_model6), breaks = 30)
```
```{r, echo=FALSE}
plot(weighted_model6, which=2)
```


```{r, echo=FALSE}
set.seed(26)
sample_res <- sample(residuals(weighted_model6), 5000)
shapiro.test(sample_res)
```

##Outliers

```{r, echo=FALSE}
plot(weighted_model6, which=5)
```

```{r, echo=FALSE}
superconductivity[cooks.distance(weighted_model6)> 0.5,]
```
```{r, echo=FALSE}
plot(weighted_model6,pch=18,col="red",which=c(4))
```

```{r, echo=FALSE}
lev=hatvalues(weighted_model6)
p = length(coef(weighted_model6))
n = nrow(superconductivity)
outlier2p = lev[lev>(2*p/n)]
outlier3p = lev[lev>(3*p/n)]
print(length(outlier2p))
print(length(outlier3p))
```

## 2.4. Contributions

# 3. MAIN RESULTS OF THE ANALYSIS

## 3.1. Results

# 4. CONCLUSION AND DISCUSSION

## 4.1. Approach
## 4.2 Future Work

# 5. REFERENCES

1. CERN, *Superconductivity*, Retrieved from <https://home.cern/science/engineering/superconductivity>, [Accessed: Nov 8, 2024].

2. Questions and Answers in MRI, *Superconducting Magnets*, Retrieved from <https://mriquestions.com/superconductive-design.html>, [Accessed: Nov 8, 2024].

3. Pennylane, *Quantum Computing with Superconducting Qubits*, Retrieved from <https://pennylane.ai/qml/demos/tutorial_sc_qubits/>, [Accessed: Nov 8, 2024].

4. SN Applied Sciences, *Prediction of Critical Temperature and New Superconducting Materials*, Retrieved from <https://link.springer.com/article/10.1007/s42452-020-03266-0?form=MG0AV3>, [Accessed: Nov 29, 2024].

5. MDPI Open Access Journals, *Predictive Modeling of Critical Temperatures in Superconducting Materials*, Retrieved from <https://www.mdpi.com/1420-3049/26/1/8?form=MG0AV3>, [Accessed: Nov 29, 2024].

6. Cornell University, *The First Room-Temperature Ambient-Pressure Superconductor*, Retrieved from <https://arxiv.org/abs/2307.12008>, [Accessed: Nov 29, 2024].

7. CBC, *Claims of Revolutionary Superconductor LK-99 Are Meeting Resistance: Here's What You Need to Know*, Retrieved from <https://www.cbc.ca/news/science/lk99-superconductor-resistance-explainer-1.6929966>, [Accessed: Nov 29, 2024].
