---
title: "project"
output: pdf_document
date: "2024-11-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

APPENDIX

```{r}
library(GGally)
library(ggplot2)
library(mctest)
library(olsrr)

plot_ggpairs <- function(data) {
  ggpairs(
    data,
    lower = list(
      continuous = wrap("smooth", method = "loess", color = "red"),
      combo = "facethist",
      discrete = "facetbar",
      na = "na"
    ),
    upper = list(
      continuous = "cor"
    ),
    diag = list(
      continuous = "densityDiag"
    ),
    progress = FALSE
  ) +
    theme_bw()
}
```

```{r}
superconductivity = read.csv("../data/train.csv")
head(superconductivity)
```

```{r}
summary(superconductivity)
```

```{r}
str(superconductivity)
```

```{r}
temp_model_additive = lm(critical_temp~., data=superconductivity)
summary(temp_model_additive)
```

All non-significant ($\alpha$ = 0.05) variables will be removed manually:

```{r}
temp_model_additive_reduced_1 = lm(critical_temp~.-wtd_range_Density, data=superconductivity)
summary(temp_model_additive_reduced_1)
```

```{r}
temp_model_additive_reduced_2 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density,
                data=superconductivity)
summary(temp_model_additive_reduced_2)
```

```{r}
temp_model_additive_reduced_3 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity, data=superconductivity)
summary(temp_model_additive_reduced_3)
```

```{r}
temp_model_additive_reduced_4 = lm(critical_temp~.-wtd_range_Density
                -wtd_mean_Density-wtd_std_ThermalConductivity
                -wtd_entropy_ThermalConductivity, data=superconductivity)
summary(temp_model_additive_reduced_4)
```

```{r}
temp_model_additive_reduced_5 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius, data=superconductivity)
summary(temp_model_additive_reduced_5)
```

```{r}
temp_model_additive_reduced_6 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass, data=superconductivity)
summary(temp_model_additive_reduced_6)
```

```{r}
temp_model_additive_reduced_7 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass,
                data=superconductivity)
summary(temp_model_additive_reduced_7)
```

```{r}
temp_model_additive_reduced_8 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence, data=superconductivity)
summary(temp_model_additive_reduced_8)
```

```{r}
temp_model_additive_reduced_9 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence-wtd_std_fie, data=superconductivity)
summary(temp_model_additive_reduced_9)
```

```{r}
temp_model_additive_reduced_10 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass
                -wtd_range_atomic_mass-wtd_range_Valence
                -wtd_std_fie-wtd_std_atomic_mass, data=superconductivity)
summary(temp_model_additive_reduced_10)
```

```{r}
temp_model_additive_reduced_11 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence-wtd_std_fie-wtd_std_atomic_mass
                -entropy_ElectronAffinity, data=superconductivity)
summary(temp_model_additive_reduced_11)
```

```{r}
temp_model_additive_reduced_12 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence-wtd_std_fie-wtd_std_atomic_mass
                -entropy_ElectronAffinity-std_FusionHeat, data=superconductivity)
summary(temp_model_additive_reduced_12)
```

```{r}
temp_model_additive_reduced_13 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence-wtd_std_fie-wtd_std_atomic_mass
                -entropy_ElectronAffinity-std_FusionHeat-mean_Valence, 
                data=superconductivity)
summary(temp_model_additive_reduced_13)
```

```{r}
temp_model_additive_reduced_14 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence-wtd_std_fie-wtd_std_atomic_mass
                -entropy_ElectronAffinity-std_FusionHeat-mean_Valence
                -std_Valence, data=superconductivity)
summary(temp_model_additive_reduced_14)
```

The following is the model including all significant variables:

```{r}
temp_model_additive_reduced_15 = lm(critical_temp~.-wtd_range_Density-wtd_mean_Density
                -wtd_std_ThermalConductivity-wtd_entropy_ThermalConductivity
                -gmean_atomic_radius-wtd_entropy_atomic_mass-wtd_range_atomic_mass
                -wtd_range_Valence-wtd_std_fie-wtd_std_atomic_mass-entropy_ElectronAffinity
                -std_FusionHeat-mean_Valence-std_Valence-wtd_mean_Valence,
                data=superconductivity)
summary(temp_model_additive_reduced_15)
```

To identify correlations between predictor variables (potential multicollinearity):

```{r}
atomic_mass = superconductivity[, c("mean_atomic_mass", "wtd_mean_atomic_mass",
                                    "gmean_atomic_mass", "wtd_gmean_atomic_mass",
                                    "entropy_atomic_mass", "range_atomic_mass",
                                    "std_atomic_mass")]
plot_ggpairs(atomic_mass)
```

```{r}
fie = superconductivity[, c("mean_fie", "wtd_mean_fie", "gmean_fie", "wtd_gmean_fie",
                            "entropy_fie", "wtd_entropy_fie", "range_fie",
                            "wtd_range_fie", "std_fie")]
plot_ggpairs(fie)
```

```{r}
atomic_radius = superconductivity[, c("mean_atomic_radius", "wtd_mean_atomic_radius",
                                      "wtd_gmean_atomic_radius", "entropy_atomic_radius",
                                      "wtd_entropy_atomic_radius", "range_atomic_radius",
                                      "wtd_range_atomic_radius", "std_atomic_radius",
                                      "wtd_std_atomic_radius" )]
plot_ggpairs(atomic_radius)
```

```{r}
density = superconductivity[, c("mean_Density", "gmean_Density", "wtd_gmean_Density",
                                "entropy_Density", "wtd_entropy_Density",
                                "range_Density", "std_Density", "wtd_std_Density")]
plot_ggpairs(density)
```

```{r}
ElectronAffinity = superconductivity[, c("mean_ElectronAffinity", "wtd_mean_ElectronAffinity",
                                         "gmean_ElectronAffinity", "wtd_gmean_ElectronAffinity",
                                         "wtd_entropy_ElectronAffinity", "range_ElectronAffinity",
                                         "wtd_range_ElectronAffinity", "std_ElectronAffinity",
                                         "wtd_std_ElectronAffinity")]
plot_ggpairs(ElectronAffinity)
```

```{r}
FusionHeat = superconductivity[, c("mean_FusionHeat", "wtd_mean_FusionHeat",
                                   "gmean_FusionHeat", "wtd_gmean_FusionHeat",
                                   "entropy_FusionHeat", "wtd_entropy_FusionHeat",
                                   "range_FusionHeat", "wtd_range_FusionHeat",
                                   "wtd_std_FusionHeat")]
plot_ggpairs(FusionHeat)
```

```{r}
ThermalConductivity = superconductivity[, c("mean_ThermalConductivity",
                                            "wtd_mean_ThermalConductivity",
                                            "gmean_ThermalConductivity",
                                            "wtd_gmean_ThermalConductivity",
                                            "entropy_ThermalConductivity",
                                            "range_ThermalConductivity",
                                            "wtd_range_ThermalConductivity",
                                            "std_ThermalConductivity")]
plot_ggpairs(ThermalConductivity)
```

```{r}
Valence = superconductivity[, c("gmean_Valence", "wtd_gmean_Valence", "entropy_Valence",
                                "wtd_entropy_Valence", "range_Valence", "wtd_std_Valence")]
plot_ggpairs(Valence)
```

All highly correlated (> 0.9) variables will be removed:

```{r}
temp_model_additive_reduced_16 = lm(critical_temp~number_of_elements+mean_atomic_mass
                         +wtd_mean_atomic_mass+entropy_atomic_mass+range_atomic_mass
                         +mean_fie+wtd_mean_fie+entropy_fie+wtd_entropy_fie
                         +range_fie+wtd_range_fie+mean_atomic_radius
                         +wtd_mean_atomic_radius+entropy_atomic_radius
                         +range_atomic_radius+wtd_range_atomic_radius+mean_Density
                         +gmean_Density+entropy_Density+wtd_entropy_Density
                         +range_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity
                         +range_ElectronAffinity+wtd_range_ElectronAffinity
                         +wtd_std_ElectronAffinity+mean_FusionHeat+wtd_gmean_FusionHeat
                         +entropy_FusionHeat+wtd_entropy_FusionHeat+range_FusionHeat
                         +wtd_range_FusionHeat+mean_ThermalConductivity
                         +wtd_mean_ThermalConductivity+gmean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +range_ThermalConductivity+wtd_range_ThermalConductivity
                         +gmean_Valence+entropy_Valence+range_Valence+wtd_std_Valence,
                         data=superconductivity)
summary(temp_model_additive_reduced_16)
```

```{r}
temp_model_additive_reduced_17 = lm(critical_temp~number_of_elements+mean_atomic_mass
                         +wtd_mean_atomic_mass+entropy_atomic_mass+range_atomic_mass
                         +mean_fie+wtd_mean_fie+entropy_fie+wtd_entropy_fie+range_fie
                         +wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                         +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                         +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                         +range_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity
                         +range_ElectronAffinity+wtd_range_ElectronAffinity
                         +wtd_std_ElectronAffinity+wtd_gmean_FusionHeat+entropy_FusionHeat
                         +wtd_entropy_FusionHeat+range_FusionHeat+wtd_range_FusionHeat
                         +mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +gmean_ThermalConductivity+wtd_gmean_ThermalConductivity
                         +entropy_ThermalConductivity+range_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+entropy_Valence
                         +range_Valence+wtd_std_Valence, data=superconductivity)
summary(temp_model_additive_reduced_17)
```

```{r}
temp_model_additive_reduced_18 = lm(critical_temp~number_of_elements+mean_atomic_mass
                         +wtd_mean_atomic_mass+entropy_atomic_mass+range_atomic_mass
                         +mean_fie+wtd_mean_fie+entropy_fie+wtd_entropy_fie+range_fie
                         +wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                         +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                         +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                         +range_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity
                         +range_ElectronAffinity+wtd_range_ElectronAffinity
                         +wtd_std_ElectronAffinity+wtd_gmean_FusionHeat+entropy_FusionHeat
                         +wtd_entropy_FusionHeat+range_FusionHeat+wtd_range_FusionHeat
                         +mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +gmean_ThermalConductivity+wtd_gmean_ThermalConductivity
                         +entropy_ThermalConductivity+wtd_range_ThermalConductivity
                         +gmean_Valence+ entropy_Valence+range_Valence+wtd_std_Valence,
                         data=superconductivity)
summary(temp_model_additive_reduced_18)
```

```{r}
temp_model_additive_reduced_19 = lm(critical_temp~number_of_elements+mean_atomic_mass
                         +wtd_mean_atomic_mass+entropy_atomic_mass+range_atomic_mass
                         +mean_fie+wtd_mean_fie+entropy_fie+wtd_entropy_fie+range_fie
                         +wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                         +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                         +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                         +range_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity
                         +range_ElectronAffinity+wtd_range_ElectronAffinity
                         +wtd_std_ElectronAffinity+wtd_gmean_FusionHeat+entropy_FusionHeat
                         +wtd_entropy_FusionHeat+range_FusionHeat+wtd_range_FusionHeat
                         +mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +gmean_ThermalConductivity+wtd_gmean_ThermalConductivity
                         +entropy_ThermalConductivity+wtd_range_ThermalConductivity
                         +gmean_Valence+range_Valence+wtd_std_Valence, data=superconductivity)
summary(temp_model_additive_reduced_19)
```

```{r}
temp_model_additive_reduced_20 = lm(critical_temp~number_of_elements+mean_atomic_mass
                         +wtd_mean_atomic_mass+entropy_atomic_mass+range_atomic_mass
                         +mean_fie+wtd_mean_fie+entropy_fie+wtd_entropy_fie+range_fie
                         +wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                         +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                         +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                         +mean_ElectronAffinity+wtd_mean_ElectronAffinity+gmean_ElectronAffinity
                         +wtd_entropy_ElectronAffinity+range_ElectronAffinity
                         +wtd_range_ElectronAffinity+wtd_std_ElectronAffinity
                         +wtd_gmean_FusionHeat+entropy_FusionHeat+wtd_entropy_FusionHeat
                         +range_FusionHeat+wtd_range_FusionHeat+mean_ThermalConductivity
                         +wtd_mean_ThermalConductivity+gmean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+range_Valence
                         +wtd_std_Valence, data=superconductivity)
summary(temp_model_additive_reduced_20)
```

```{r}
temp_model_additive_reduced_21 = lm(critical_temp~number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                         +entropy_atomic_mass+range_atomic_mass+mean_fie+wtd_mean_fie
                         +entropy_fie+wtd_entropy_fie+range_fie+wtd_range_fie+mean_atomic_radius
                         +wtd_mean_atomic_radius+entropy_atomic_radius+range_atomic_radius
                         +wtd_range_atomic_radius+mean_Density+gmean_Density+entropy_Density
                         +wtd_entropy_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity+range_ElectronAffinity
                         +wtd_range_ElectronAffinity+wtd_std_ElectronAffinity+wtd_gmean_FusionHeat
                         +entropy_FusionHeat+wtd_entropy_FusionHeat+range_FusionHeat
                         +wtd_range_FusionHeat+mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+range_Valence+wtd_std_Valence,
                         data=superconductivity)
summary(temp_model_additive_reduced_21)
```

```{r}
temp_model_additive_reduced_22 = lm(critical_temp~number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                         +entropy_atomic_mass+range_atomic_mass+wtd_mean_fie+entropy_fie
                         +wtd_entropy_fie+range_fie+wtd_range_fie+mean_atomic_radius
                         +wtd_mean_atomic_radius+entropy_atomic_radius+range_atomic_radius
                         +wtd_range_atomic_radius+mean_Density+gmean_Density+entropy_Density
                         +wtd_entropy_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity+range_ElectronAffinity
                         +wtd_range_ElectronAffinity+wtd_std_ElectronAffinity+wtd_gmean_FusionHeat
                         +entropy_FusionHeat+wtd_entropy_FusionHeat+range_FusionHeat
                         +wtd_range_FusionHeat+mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+range_Valence+wtd_std_Valence,
                         data=superconductivity)
summary(temp_model_additive_reduced_22)
```

```{r}
temp_model_additive_reduced_23 = lm(critical_temp~number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                         +entropy_atomic_mass+range_atomic_mass+wtd_mean_fie+entropy_fie
                         +wtd_entropy_fie+wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                         +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                         +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                         +mean_ElectronAffinity+wtd_mean_ElectronAffinity+gmean_ElectronAffinity
                         +wtd_entropy_ElectronAffinity+range_ElectronAffinity+wtd_range_ElectronAffinity
                         +wtd_std_ElectronAffinity+wtd_gmean_FusionHeat+entropy_FusionHeat
                         +wtd_entropy_FusionHeat+range_FusionHeat+wtd_range_FusionHeat
                         +mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+range_Valence+wtd_std_Valence,
                         data=superconductivity)
summary(temp_model_additive_reduced_23)
```

```{r}
temp_model_additive_reduced_24 = lm(critical_temp~number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                         +entropy_atomic_mass+range_atomic_mass+wtd_mean_fie+entropy_fie
                         +wtd_entropy_fie+range_fie+wtd_range_fie+mean_atomic_radius
                         +wtd_mean_atomic_radius+entropy_atomic_radius+range_atomic_radius
                         +wtd_range_atomic_radius+mean_Density+gmean_Density+entropy_Density
                         +wtd_entropy_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
                         +gmean_ElectronAffinity+wtd_entropy_ElectronAffinity+range_ElectronAffinity
                         +wtd_range_ElectronAffinity+wtd_gmean_FusionHeat+entropy_FusionHeat
                         +wtd_entropy_FusionHeat+range_FusionHeat+wtd_range_FusionHeat
                         +mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+range_Valence
                         +wtd_std_Valence, data=superconductivity)
summary(temp_model_additive_reduced_24)
```

```{r}
temp_model_additive_reduced_25 = lm(critical_temp~number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                         +entropy_atomic_mass+range_atomic_mass+wtd_mean_fie+entropy_fie
                         +wtd_entropy_fie+wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                         +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                         +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                         +mean_ElectronAffinity+wtd_mean_ElectronAffinity+gmean_ElectronAffinity
                         +wtd_entropy_ElectronAffinity+range_ElectronAffinity+wtd_range_ElectronAffinity
                         +wtd_gmean_FusionHeat+entropy_FusionHeat+wtd_entropy_FusionHeat+range_FusionHeat
                         +wtd_range_FusionHeat+mean_ThermalConductivity+wtd_mean_ThermalConductivity
                         +wtd_gmean_ThermalConductivity+entropy_ThermalConductivity
                         +wtd_range_ThermalConductivity+gmean_Valence+range_Valence+wtd_std_Valence,
                         data=superconductivity)
summary(temp_model_additive_reduced_25)
```

```{r}
temp_model_additive_reduced_26 = lm(critical_temp~number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                          +entropy_atomic_mass+range_atomic_mass+wtd_mean_fie+entropy_fie
                          +wtd_entropy_fie+wtd_range_fie+mean_atomic_radius+wtd_mean_atomic_radius
                          +entropy_atomic_radius+range_atomic_radius+wtd_range_atomic_radius
                          +mean_Density+gmean_Density+entropy_Density+wtd_entropy_Density
                          +mean_ElectronAffinity+wtd_mean_ElectronAffinity+gmean_ElectronAffinity
                          +wtd_entropy_ElectronAffinity+range_ElectronAffinity+wtd_range_ElectronAffinity
                          +wtd_gmean_FusionHeat+entropy_FusionHeat+wtd_entropy_FusionHeat
                          +range_FusionHeat+wtd_range_FusionHeat+mean_ThermalConductivity
                          +wtd_mean_ThermalConductivity+wtd_gmean_ThermalConductivity
                          +entropy_ThermalConductivity+wtd_range_ThermalConductivity
                          +range_Valence+wtd_std_Valence, data=superconductivity)
summary(temp_model_additive_reduced_26)
```

```{r}
imcdiag(temp_model_additive_reduced_26, method="VIF")
```

```{r}
reduced_data_part_1 = superconductivity[, c("number_of_elements", "mean_atomic_mass",
                                            "wtd_mean_atomic_mass", "entropy_atomic_mass",
                                            "wtd_mean_fie", "entropy_fie",
                                            "wtd_entropy_fie", "wtd_range_fie")]
plot_ggpairs(reduced_data_part_1)
```

```{r}
reduced_data_part_2 = superconductivity[, c("wtd_mean_atomic_radius", "entropy_atomic_radius",
                                            "range_atomic_radius", "mean_Density",
                                            "gmean_Density", "entropy_Density",
                                            "wtd_entropy_Density")]
plot_ggpairs(reduced_data_part_2)
```

```{r}
reduced_data_part_3 = superconductivity[, c("mean_ElectronAffinity", "wtd_mean_ElectronAffinity",
                                            "gmean_ElectronAffinity", "wtd_entropy_ElectronAffinity",
                                            "wtd_range_ElectronAffinity", "entropy_FusionHeat",
                                            "wtd_entropy_FusionHeat", "wtd_mean_ThermalConductivity",
                                            "wtd_range_ThermalConductivity")]
plot_ggpairs(reduced_data_part_3)
```

```{r}
temp_model_reduced_27 = lm(critical_temp ~ number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
             +wtd_mean_fie+wtd_entropy_fie+wtd_range_fie+wtd_mean_atomic_radius
             +entropy_atomic_radius+range_atomic_radius+mean_Density+wtd_entropy_Density
             +mean_ElectronAffinity+wtd_mean_ElectronAffinity+wtd_entropy_ElectronAffinity
             +wtd_range_ElectronAffinity+entropy_FusionHeat+wtd_mean_ThermalConductivity,
             data=superconductivity)
summary(temp_model_reduced_27)
```

```{r}
imcdiag(temp_model_additive_reduced_27, method="VIF")
```

```{r}
reduced_data_part_4 = superconductivity[, c("number_of_elements", "wtd_mean_fie",
                                            "wtd_entropy_fie", "wtd_range_fie",
                                            "entropy_atomic_radius", "wtd_mean_ElectronAffinity",
                                            "wtd_range_ElectronAffinity", "entropy_FusionHeat")]
plot_ggpairs(reduced_data_part_4)
```

```{r}
temp_model_additive_reduced_28 = lm(critical_temp ~ number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
             +wtd_mean_fie+wtd_entropy_fie+wtd_range_fie+wtd_mean_atomic_radius
             +range_atomic_radius+mean_Density+wtd_entropy_Density+mean_ElectronAffinity
             +wtd_mean_ElectronAffinity+wtd_entropy_ElectronAffinity+wtd_mean_ThermalConductivity,
             data=superconductivity)
summary(temp_model_additive_reduced_28)
```

```{r}
final_model_additive = lm(critical_temp ~ number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
             +wtd_mean_fie+wtd_entropy_fie+wtd_mean_atomic_radius+range_atomic_radius
             +mean_Density+wtd_entropy_Density+mean_ElectronAffinity+wtd_mean_ElectronAffinity
             +wtd_entropy_ElectronAffinity+wtd_mean_ThermalConductivity, data=superconductivity)
summary(final_model_additive)
```

```{r}
imcdiag(final_model_additive, method="VIF")
```

According to the output, the predictors are not affected by multicollinearity.

```{r}
anova(final_model_additive, temp_model_additive)
```

The model will be expanded to include interaction terms:

```{r}
temp_model_int = lm(critical_temp ~ (number_of_elements+mean_atomic_mass+wtd_mean_atomic_mass
                                  +wtd_mean_fie+wtd_entropy_fie+wtd_mean_atomic_radius
                                  +range_atomic_radius+mean_Density+wtd_entropy_Density
                                  +mean_ElectronAffinity+wtd_mean_ElectronAffinity
                                  +wtd_entropy_ElectronAffinity+wtd_mean_ThermalConductivity)^2,
                 data=superconductivity)
summary(temp_model_int)
```

Non-significant variables will be removed using a forward selection approach:

```{r}
temp_model_int_reduced_1 = ols_step_forward_p(temp_model_int, p_val=0.01, details=FALSE)
summary(temp_model_int_reduced_1$model)
```

```{r}
temp_model_int_reduced_2 = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                     +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                     +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density
                     +wtd_mean_atomic_mass+mean_ElectronAffinity+mean_Density
                     +number_of_elements+wtd_entropy_fie+range_atomic_radius
                     +wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                     +range_atomic_radius:wtd_entropy_Density
                     +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                     +range_atomic_radius:wtd_mean_ElectronAffinity
                     +wtd_mean_fie:wtd_mean_ThermalConductivity
                     +number_of_elements:wtd_mean_atomic_mass
                     +range_atomic_radius:mean_Density+mean_atomic_mass:range_atomic_radius
                     +wtd_entropy_fie:wtd_mean_atomic_radius
                     +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                     +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                     +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                     +number_of_elements:wtd_mean_ThermalConductivity
                     +range_atomic_radius:mean_ElectronAffinity
                     +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                     +wtd_mean_atomic_radius:range_atomic_radius
                     +number_of_elements:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                     +number_of_elements:wtd_mean_ElectronAffinity
                     +number_of_elements:mean_ElectronAffinity+wtd_mean_atomic_mass:wtd_entropy_fie
                     +mean_atomic_mass:wtd_mean_fie+mean_atomic_mass:wtd_mean_atomic_radius
                     +wtd_mean_fie:mean_Density+range_atomic_radius:wtd_entropy_ElectronAffinity
                     +mean_atomic_mass:wtd_entropy_Density+wtd_entropy_Density:wtd_mean_ElectronAffinity
                     +wtd_entropy_fie:wtd_mean_ThermalConductivity+wtd_mean_fie:wtd_mean_atomic_radius
                     +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity+mean_atomic_mass:wtd_mean_ElectronAffinity
                     +mean_Density:wtd_mean_ElectronAffinity+wtd_mean_atomic_radius:mean_ElectronAffinity
                     +wtd_mean_atomic_mass:range_atomic_radius+wtd_entropy_Density:wtd_mean_ThermalConductivity
                     +mean_Density:wtd_mean_ThermalConductivity+mean_atomic_mass:wtd_mean_ThermalConductivity
                     +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                     +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                     +number_of_elements:wtd_entropy_ElectronAffinity+number_of_elements:wtd_entropy_fie
                     +wtd_mean_atomic_mass:wtd_entropy_Density+wtd_mean_atomic_radius:wtd_entropy_Density
                     +mean_ElectronAffinity:wtd_mean_ElectronAffinity+wtd_mean_fie:mean_ElectronAffinity
                     +number_of_elements:mean_Density+wtd_entropy_fie:mean_Density
                     +mean_Density:wtd_entropy_Density+wtd_mean_fie:wtd_entropy_ElectronAffinity
                     +number_of_elements:wtd_mean_fie+wtd_mean_fie:wtd_mean_ElectronAffinity
                     +wtd_entropy_fie:wtd_entropy_ElectronAffinity+wtd_entropy_fie:wtd_entropy_Density
                     +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_int_reduced_2)
```

The remaining non-significant ($\alpha$ = 0.01) variables will be removed manually:

```{r}
temp_model_int_reduced_3 = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                     +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                     +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density
                     +wtd_mean_atomic_mass+mean_ElectronAffinity+mean_Density+number_of_elements
                     +wtd_entropy_fie+range_atomic_radius+wtd_mean_ThermalConductivity
                     +wtd_mean_fie:range_atomic_radius+range_atomic_radius:wtd_entropy_Density
                     +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                     +range_atomic_radius:wtd_mean_ElectronAffinity
                     +wtd_mean_fie:wtd_mean_ThermalConductivity
                     +number_of_elements:wtd_mean_atomic_mass+range_atomic_radius:mean_Density
                     +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                     +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                     +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                     +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                     +number_of_elements:wtd_mean_ThermalConductivity
                     +range_atomic_radius:mean_ElectronAffinity+mean_atomic_mass:wtd_entropy_fie
                     +mean_atomic_mass:wtd_entropy_ElectronAffinity+wtd_mean_atomic_radius:range_atomic_radius
                     +number_of_elements:wtd_mean_atomic_radius+number_of_elements:wtd_mean_ElectronAffinity
                     +number_of_elements:mean_ElectronAffinity+wtd_mean_atomic_mass:wtd_entropy_fie
                     +mean_atomic_mass:wtd_mean_fie+mean_atomic_mass:wtd_mean_atomic_radius
                     +wtd_mean_fie:mean_Density+range_atomic_radius:wtd_entropy_ElectronAffinity
                     +mean_atomic_mass:wtd_entropy_Density+wtd_entropy_Density:wtd_mean_ElectronAffinity
                     +wtd_entropy_fie:wtd_mean_ThermalConductivity+wtd_mean_fie:wtd_mean_atomic_radius
                     +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity+mean_atomic_mass:wtd_mean_ElectronAffinity
                     +mean_Density:wtd_mean_ElectronAffinity+wtd_mean_atomic_radius:mean_ElectronAffinity
                     +wtd_mean_atomic_mass:range_atomic_radius+wtd_entropy_Density:wtd_mean_ThermalConductivity
                     +mean_Density:wtd_mean_ThermalConductivity+mean_atomic_mass:wtd_mean_ThermalConductivity
                     +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                     +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                     +number_of_elements:wtd_entropy_ElectronAffinity+number_of_elements:wtd_entropy_fie
                     +wtd_mean_atomic_mass:wtd_entropy_Density+wtd_mean_atomic_radius:wtd_entropy_Density
                     +mean_ElectronAffinity:wtd_mean_ElectronAffinity+wtd_mean_fie:mean_ElectronAffinity
                     +number_of_elements:mean_Density+wtd_entropy_fie:mean_Density
                     +mean_Density:wtd_entropy_Density+wtd_mean_fie:wtd_entropy_ElectronAffinity
                     +number_of_elements:wtd_mean_fie+wtd_mean_fie:wtd_mean_ElectronAffinity
                     +wtd_entropy_fie:wtd_entropy_ElectronAffinity+wtd_entropy_fie:wtd_entropy_Density
                     +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(temp_model_int_reduced_3)
```

```{r}
final_model_int = lm(critical_temp ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +range_atomic_radius:wtd_mean_ElectronAffinity+wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass+range_atomic_radius:mean_Density
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius+wtd_mean_fie:mean_Density
                 +range_atomic_radius:wtd_entropy_ElectronAffinity+mean_atomic_mass:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_mean_ThermalConductivity+wtd_mean_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity+mean_Density:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +wtd_entropy_Density:wtd_mean_ThermalConductivity+mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_entropy_ElectronAffinity+number_of_elements:wtd_entropy_fie
                 +wtd_mean_atomic_mass:wtd_entropy_Density+wtd_mean_atomic_radius:wtd_entropy_Density
                 +mean_ElectronAffinity:wtd_mean_ElectronAffinity+wtd_mean_fie:mean_ElectronAffinity
                 +number_of_elements:mean_Density+wtd_entropy_fie:mean_Density
                 +mean_Density:wtd_entropy_Density+wtd_mean_fie:wtd_entropy_ElectronAffinity
                 +number_of_elements:wtd_mean_fie+wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_ElectronAffinity+wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(final_model_int)
```

```{r}
anova(final_model_int, temp_model_int)
```

### Linearity Assumption

```{r}
ggplot(final_model_int, aes(x=.fitted, y=.resid)) + geom_point() + geom_smooth() +
  geom_hline(yintercept=0) 
```

```{r}
final_data = superconductivity[, c("critical_temp", "wtd_mean_ElectronAffinity", "wtd_mean_atomic_radius",
                                   "mean_atomic_mass", "wtd_mean_fie", "wtd_entropy_ElectronAffinity",
                                   "wtd_entropy_Density", "wtd_mean_atomic_mass",
                                   "mean_ElectronAffinity", "mean_Density", "number_of_elements",
                                   "wtd_entropy_fie", "range_atomic_radius", "wtd_mean_ThermalConductivity")]
plot_ggpairs(final_data)
```

```{r}
final_model_linearity_ass = lm(log(critical_temp) ~ range_atomic_radius:wtd_mean_ThermalConductivity
                 +wtd_mean_ElectronAffinity+wtd_mean_atomic_radius+mean_atomic_mass
                 +wtd_mean_fie+wtd_entropy_ElectronAffinity+wtd_entropy_Density+wtd_mean_atomic_mass
                 +mean_ElectronAffinity+mean_Density+number_of_elements+wtd_entropy_fie
                 +range_atomic_radius+wtd_mean_ThermalConductivity+wtd_mean_fie:range_atomic_radius
                 +range_atomic_radius:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_entropy_ElectronAffinity
                 +range_atomic_radius:wtd_mean_ElectronAffinity+wtd_mean_fie:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_atomic_mass+range_atomic_radius:mean_Density
                 +mean_atomic_mass:range_atomic_radius+wtd_entropy_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_entropy_ElectronAffinity
                 +wtd_mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_mean_atomic_mass:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_entropy_ElectronAffinity
                 +wtd_mean_atomic_radius:range_atomic_radius+number_of_elements:wtd_mean_atomic_radius
                 +number_of_elements:wtd_mean_ElectronAffinity+number_of_elements:mean_ElectronAffinity
                 +wtd_mean_atomic_mass:wtd_entropy_fie+mean_atomic_mass:wtd_mean_fie
                 +mean_atomic_mass:wtd_mean_atomic_radius+wtd_mean_fie:mean_Density
                 +range_atomic_radius:wtd_entropy_ElectronAffinity+mean_atomic_mass:wtd_entropy_Density
                 +wtd_entropy_Density:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_mean_ThermalConductivity+wtd_mean_fie:wtd_mean_atomic_radius
                 +wtd_mean_atomic_radius:wtd_mean_ElectronAffinity
                 +mean_atomic_mass:wtd_mean_ElectronAffinity+mean_Density:wtd_mean_ElectronAffinity
                 +wtd_mean_atomic_radius:mean_ElectronAffinity+wtd_mean_atomic_mass:range_atomic_radius
                 +wtd_entropy_Density:wtd_mean_ThermalConductivity+mean_Density:wtd_mean_ThermalConductivity
                 +mean_atomic_mass:wtd_mean_ThermalConductivity
                 +mean_ElectronAffinity:wtd_mean_ThermalConductivity
                 +wtd_entropy_ElectronAffinity:wtd_mean_ThermalConductivity
                 +number_of_elements:wtd_entropy_ElectronAffinity+number_of_elements:wtd_entropy_fie
                 +wtd_mean_atomic_mass:wtd_entropy_Density+wtd_mean_atomic_radius:wtd_entropy_Density
                 +mean_ElectronAffinity:wtd_mean_ElectronAffinity+wtd_mean_fie:mean_ElectronAffinity
                 +number_of_elements:mean_Density+wtd_entropy_fie:mean_Density
                 +mean_Density:wtd_entropy_Density+wtd_mean_fie:wtd_entropy_ElectronAffinity
                 +number_of_elements:wtd_mean_fie+wtd_mean_fie:wtd_mean_ElectronAffinity
                 +wtd_entropy_fie:wtd_entropy_ElectronAffinity+wtd_entropy_fie:wtd_entropy_Density
                 +wtd_entropy_fie:mean_ElectronAffinity, data=superconductivity)
summary(final_model_linearity_ass)
```

```{r}
ggplot(final_model_linearity_ass, aes(x=.fitted, y=.resid)) + geom_point() + geom_smooth() +
  geom_hline(yintercept=0)
```